Inefficient Concessions and Mediation

### 2021-01-12 notes.tex
update to-do section

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item NEXT STEP: check condition for sustainable $e=1$ but prefer mediator with $e < 1$ 
						\begin{itemize}
							\item I've found parameterizations where $e=1$ is preferred (P5)
							\item Try to find a parameterization that shows the reverse (counterexample to my hypothesis that if $e=1$ is sustainable, you never invoke mediator) or see if I can prove that it never happens
						\end{itemize}
					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
						\begin{itemize}
							\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE.
							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
						\end{itemize}
				\item When $g^1$ turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g^1$, not sure we'd need the mediator? It's not about $g^1$, but the $\de_h^1$ condition.
					\begin{itemize}
						\item When $g^1$ is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
						\item I need a formal result to see clearly what is going on here
					\end{itemize}
			\end{itemize}

>>>>

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
						\begin{itemize}
							\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE.
							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
						\end{itemize}
				\item When $g^1$ turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g^1$, not sure we'd need the mediator? It's not about $g^1$, but the $\de_h^1$ condition.
					\begin{itemize}
						\item When $g^1$ is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
						\item I need a formal result to see clearly what is going on here
					\end{itemize}
			\end{itemize}
